---
title: "Journal (reproducible report)"
author: "Qianyun Wang"
date: "2020-11-24"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    code_folding: hide
---
```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE,
	cache = TRUE
)
```

***
# Intro to the tidyverse

Last compiled: `r Sys.Date()`

course result and challenge result

## Course Result

> **Sales by Year and Category Analyse**

***

```{r plot, fig.width=7, fig.height=4,echo = FALSE}
# 1.0 Load libraries ----
library(tidyverse)
library(readxl)

# 2.0 Importing Files ----
bikes_tbl <- read_excel(path="~/Desktop/TUHH/Bussiness Data Science Basic/DS_101/00_data/01_bike_sales/01_raw_data/bikes.xlsx") 
order_tbl <- read_excel(path = "~/Desktop/TUHH/Bussiness Data Science Basic/DS_101/00_data/01_bike_sales/01_raw_data/orderlines.xlsx")
bikeshop_tbl <-read_excel(path = "~/Desktop/TUHH/Bussiness Data Science Basic/DS_101/00_data/01_bike_sales/01_raw_data/bikeshops.xlsx")

# 4.0 Joining Data ----
bike_orderlines_joined_tbl <- order_tbl %>%
  left_join(bikes_tbl,by=c('product.id'='bike.id')) %>%
  left_join(bikeshop_tbl,by=c('customer.id'='bikeshop.id'))

# 5.0 Wrangling Data ----
bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
  separate(col= category,
           into = c('category.1','category.2','category.3'),
           sep = '-') %>%
  mutate(total.price = price * quantity) %>%
  
  select(-...1, -gender) %>%
  select(-ends_with('.id'))%>%
  bind_cols(bike_orderlines_joined_tbl %>% select(order.id))%>%
  
  select(order.id, contains('order'),contains('model'),contains('category'),
         price, quantity, total.price,
         everything()) %>%
 
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all('\\.','_'))

# 6.0 Business Insights ----
# 6.1 Sales by Year ----

# Step 1 - Manipulate
library(lubridate)
sales_by_year_tbl <- bike_orderlines_wrangled_tbl %>%
  select(order_date, total_price) %>%
  mutate(year=year(order_date))%>%
  group_by(year) %>%
  summarise(sales=sum(total_price))%>%
  
  mutate(sales_text = scales::dollar(sales, big.mark = '.',
                                    decimal.mark =',',
                                    prefix = '',
                                    suffix =" €"
                                    ))

# Step 2 - Visualize
sales_by_year_tbl %>%
  ggplot(aes(x = year, y= sales)) +
  
  geom_col(fill="#2DC6D6") +
  geom_label(aes(label=sales_text))+
  geom_smooth(method = 'lm',se=FALSE) +
  
  scale_y_continuous(labels = scales::dollar_format(big.mark ='.',
                                                    decimal.mark =',',
                                                    prefix = '',
                                                    suffix =" €" ))+
  labs(
    title = 'Revenue by year',
    subtitle = "Upward Trend",
    x="",
    y="Revenue"
  )

# 6.2 Sales by Year and Category 2 ----
# Step 1 - Manipulate

sales_by_year_cat_1_tbl <- bike_orderlines_wrangled_tbl %>%
  select(order_date, total_price, category_1) %>%
  mutate(year=year(order_date))%>%
  group_by(year, category_1) %>%
  summarise(sales = sum(total_price))%>%
  ungroup() %>%
  
  mutate(sales_text = scales::dollar(sales, big.mark = '.',
                                     decimal.mark =',',
                                     prefix = '',
                                     suffix =" €"
  ))

# Step 2 - Visualize
sales_by_year_cat_1_tbl %>%
  ggplot(aes(x=year,y=sales, fill=category_1))+
  
  geom_col()+
  geom_smooth(method = 'lm',se=FALSE) +
  
facet_wrap(~category_1)+

  scale_y_continuous(labels = scales::dollar_format(big.mark ='.',
                                                    decimal.mark =',',
                                                    prefix = '',
                                                    suffix =" €" ))+
  labs(
    title = 'Revenue by year and main category',
    subtitle = "Each product category has an upward Trend",
    fill="Main category"
  )

```

***
## Challenge Result

> **Sales by Location and Year Analyse**

> 1.Analyze the sales by location (state) with a bar plot. Since state and city are multiple features (variables), they should be split. Which state has the highes revenue?

* **Answer**: North Rhine-Westphalia

> 2.Analyze the sales by location and year (facet_wrap). Because there are 12 states with bike stores, you should get 12 plots.

* **Answer**: Both plots below.

***
```{r plot2, fig.width=10, fig.height=7,echo = FALSE}
# 1.0 Load libraries ----
library(tidyverse)
library(readxl)

# 2.0 Importing Files ----
bikes_tbl <- read_excel(path="~/Desktop/TUHH/Bussiness Data Science Basic/DS_101/00_data/01_bike_sales/01_raw_data/bikes.xlsx") 
order_tbl <- read_excel(path = "~/Desktop/TUHH/Bussiness Data Science Basic/DS_101/00_data/01_bike_sales/01_raw_data/orderlines.xlsx")
bikeshop_tbl <-read_excel(path = "~/Desktop/TUHH/Bussiness Data Science Basic/DS_101/00_data/01_bike_sales/01_raw_data/bikeshops.xlsx")

# 4.0 Joining Data ----
bike_orderlines_joined_tbl <- order_tbl %>%
  left_join(bikes_tbl,by=c('product.id'='bike.id')) %>%
  left_join(bikeshop_tbl,by=c('customer.id'='bikeshop.id'))

# Wrangling data ----
bike_orderlines_wrangled_2_tbl <- bike_orderlines_joined_tbl %>%
  separate(col= location,
           into = c('city','state'),
           sep = ',') %>%
  mutate(total.price = price * quantity) %>%
  
  select(-...1, -gender,-category) %>%
  select(-ends_with('.id'))%>%
  bind_cols(bike_orderlines_joined_tbl %>% select(order.id))%>%
  
  select(order.id, contains('order'),contains('state'),contains('city'),
         price, quantity, total.price,
         everything())

# Sales by Location ----

# Step 1 - Manipulate
sales_by_loc_tbl <- bike_orderlines_wrangled_2_tbl %>%
  select(state, total.price) %>%
  group_by(state) %>%
  summarise(sales=sum(total.price))%>%
  
  mutate(sales_text = scales::dollar(sales, big.mark = '.',
                                     decimal.mark =',',
                                     prefix = '',
                                     suffix =" €"
  ))

# Step 2 - Visualize
sales_by_loc_tbl %>%
  ggplot(aes(x = state, y= sales)) +
  
  geom_col(fill="#2DC6D6") +
  geom_label(aes(label=sales_text))+
  
  scale_y_continuous(labels = scales::dollar_format(big.mark ='.',
                                                    decimal.mark =',',
                                                    prefix = '',
                                                    suffix =" €" ))+
  
  labs(
    title = 'Sales by state',
    subtitle = "Top state: North Rhine-Westphalia",
    x="",
    y="Revenue"
  )+ 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Sales by Year and Location ----
# Step 1 - Manipulate

sales_by_year_loc_tbl <- bike_orderlines_wrangled_2_tbl %>%
  select(order.date, total.price, state) %>%
  mutate(year=year(order.date))%>%
  group_by(year, state) %>%
  summarise(sales = sum(total.price))%>%
  ungroup() %>%
  
  mutate(sales_text = scales::dollar(sales, big.mark = '.',
                                     decimal.mark =',',
                                     prefix = '',
                                     suffix =" €"
  ))

# Step 2 - Visualize
sales_by_year_loc_tbl %>%
  ggplot(aes(x=year,y=sales, fill=state))+
  
  geom_col()+
  geom_smooth(method = 'lm',se=FALSE) +
  
  facet_wrap(~state)+
  
  scale_y_continuous(labels = scales::dollar_format(big.mark ='.',
                                                    decimal.mark =',',
                                                    prefix = '',
                                                    suffix =" €" ))+
  labs(
    title = 'Revenue by year and state',
    subtitle = "Most state has an upward Trend",
    fill="State"
  )

```

***
# Data Acquisition

Last compiled: `r Sys.Date()`

## Get Data via API 
> I get the daily visit data as pv of the wikipedia page: Coronavirus_disease_2019 (https://en.wikipedia.org/w/index.php?title=Coronavirus_disease_2019&redirect=no), the time period is set to recent 10 days and can be changed in the R code freely.  The result of json format and tibble format is shown below.

```{r echo=TRUE}
library(tidyverse)
library(httr)
library(jsonlite)
library(lubridate)
library(stringr)

starting <- "20201114"
ending <- "20201124"
article_title <- 'Coronavirus_disease_2019'

url <- paste("https://wikimedia.org/api/rest_v1/metrics/pageviews/per-article/en.wikipedia/all-access/all-agents",
             article_title,
             "daily",
             starting,
             ending,
             sep = "/")

resp <-GET(url)

toJSON(fromJSON(content(resp, as="text")), pretty = TRUE)
result <- fromJSON(content(resp, as="text"))
result_tbl<-map(result, ~data.frame(.))%>%
  map_dfr(.,~mutate_all(.,as.character()))%>%
  as_tibble()%>%
  transmute(Website = project,
         Aritcle_title = article,
         Visit_type = granularity,
         Date =ymd(str_sub(timestamp, 1, -3)),
         Views=views)
result_tbl


```

***

## Bike Data of Rosebike 

> I get create a small database of MTA bike data from website rosebike, the database inclues the name and price information for all the bikes with the category MTA of this website. There are in total 22 bike information and this page only shows the first 10 rows.

```{r}
library(tidyverse) 
library(rvest)   
library(jsonlite) 
library(glue)   
library(stringi) 

url_mtb <- "https://www.rosebikes.de/fahrr%C3%A4der/mtb"
html_mtb <- read_html(url_mtb)

mtb_bike_category_tbl <- html_mtb  %>%
  
  html_nodes(css='.catalog-category-bikes__button')%>%
  html_attr('href')%>%
  enframe(name = 'position', value = 'subdirectory') %>%
  mutate(url=glue('https://www.rosebikes.de{subdirectory}'))%>%
  distinct(url)

get_mtb_bike_data <- function(url_mtb){
  
  mtb_html_bike_category <- read_html(url_mtb)
  
  mtb_bike_name_tbl<- mtb_html_bike_category %>%
    html_nodes(css= '.catalog-category-model__title')%>%
    html_text() %>%
    stringr::str_replace_all(pattern = "\\\n", replacement = "")%>%
    enframe(name = 'position', value = 'name')
    
  mtb_bike_price_tbl <- mtb_html_bike_category %>%
    html_nodes(css= '.catalog-category-model__price-current-value')%>%
    html_text() %>%
    stringr::str_replace_all(pattern = "\\\n", replacement = "")%>%
    enframe(name = 'position', value = 'price')%>%
    left_join(mtb_bike_name_tbl)
  
}

mtb_bike_category_url_vec <- mtb_bike_category_tbl %>% 
  pull(url)

mtb_bike_data_lst <- map(mtb_bike_category_url_vec, get_mtb_bike_data)


mtb_bike_data_tbl <- bind_rows(mtb_bike_data_lst) 
mtb_bike_data_tbl <- add_column(mtb_bike_data_tbl, category='MTB')
mtb_bike_data_tbl <- mtb_bike_data_tbl[c( 'category','name','price')]
mtb_bike_data_tbl

saveRDS(mtb_bike_data_tbl, "mtb_bike_data_tbl.rds")

```

***

# Data Wrangling


```{r calculation, eval= FALSE}
library(tidyverse)
library(vroom)
library(data.table)
library(tictoc)

col_patent <- list(
  patent_id = col_character(),
  patent_type = col_character(),
  number = col_character(),
  country = col_character(),
  date = col_date("%Y-%m-%d"),
  abstract = col_character(),
  title = col_character(),
  kind = col_character(),
  num_claims = col_double(),
  filename = col_character(),
  withdrawn = col_double()
)

patent_tbl <- vroom(
  file       = "patent.tsv", 
  delim      = "\t", 
  col_names  = names(col_patent),
  col_types  = col_patent,
  na         = c("", "NA", "NULL")
)


col_assignee <- list(
  assignee_id = col_character(),
  assignee_type = col_double(),
  name_first = col_character(),
  name_last = col_character(),
  organization = col_character()
)

assignee_tbl <- vroom(
  file       = "assignee.tsv", 
  delim      = "\t", 
  col_names  = names(col_assignee),
  col_types  = col_assignee,
  na         = c("", "NA", "NULL")
)

col_patent_assignee <- list(
  patent_id = col_character(),
  assignee_id = col_character(),
  location_id = col_character()
)

patent_assignee_tbl <- vroom(
  file       = "patent_assignee.tsv", 
  delim      = "\t", 
  col_names  = names(col_patent_assignee),
  col_types  = col_patent_assignee,
  na         = c("", "NA", "NULL")
)

col_uspc <- list(
  uuid = col_character(),
  patent_id = col_character(),
  mainclass_id = col_character(),
  subclass_id = col_character(),
  sequence= col_double()
)

uspc_tbl <- vroom(
  file       = "USPC.tsv", 
  delim      = "\t", 
  col_names  = names(col_uspc),
  col_types  = col_uspc,
  na         = c("", "NA", "NULL")
)


combined_p_a_data <- assignee_tbl %>%
  select(assignee_id, assignee_type, organization) %>%
  filter(assignee_type ==2) %>%
  right_join(patent_assignee_tbl,by='assignee_id') %>%
  select(patent_id, assignee_id, assignee_type, organization)
  
patent_dominance <-combined_p_a_data %>%
  filter(assignee_type ==2) %>%
  group_by(organization)%>%
  summarise(patent_num=n())%>%
  ungroup()%>%
  arrange(desc(patent_num))

write_rds(patent_dominance,'patent_dominace.rds')


combined_p_a_p_data <- patent_tbl %>%
  select(patent_id, date) %>%
  left_join(combined_p_a_data,by='patent_id') %>%
  select(patent_id, date,assignee_id, assignee_type, organization)

recent_patent_activity <-combined_p_a_p_data %>%
  filter(assignee_type ==2) %>%
  filter(year(date)== 2019)%>%
  group_by(organization)%>%
  summarise(patent_num_2019=n())%>%
  ungroup()%>%
  arrange(desc(patent_num_2019))

write_rds(recent_patent_activity,'recent_patent_activity.rds')

patent_dominance_worldwide <-combined_p_a_data %>%
  filter(assignee_type ==2 | assignee_type ==3) %>%
  group_by(organization)%>%
  summarise(patent_num=n())%>%
  ungroup()%>%
  arrange(desc(patent_num))

combined_p_a_u_data <- uspc_tbl%>%
  select(patent_id, mainclass_id)%>%
  left_join(combined_p_a_data,by= "patent_id")%>%
  select(patent_id,assignee_id,assignee_type,organization,mainclass_id)

innovation_in_tech <-combined_p_a_u_data %>%
  filter(assignee_id %in% c('org_ONzMjdbZXiKfw4L0cXl6',  
                            'org_pCbqlmAg8wlWzoi18ITD',
                            'org_eAKK85fawH0NS7AdXOig',
                            'org_g8U335TH48QmGJOIQnNl',
                            'org_EccJQIigrq4WyGinD0b8',
                            'org_rWEJSmVQtQg24yFJqVRb',
                            'org_yOSqt2KbCZQB2LRNpEKS',
                            'org_OrmhECOcsM3rq5b7Pxfe',
                            'org_f0ZEyISdLqKONLOyVOev',
                            'org_sCPx37zDCUvOnx2ptLAe'))%>%
  group_by(mainclass_id)%>%
  summarise(patent_num_mainclass=n())%>%
  ungroup()%>%
  arrange(desc(patent_num_mainclass))

write_rds(innovation_in_tech,'innovation_in_tech.rds')

```

> 1.What US company has the most patents? List the 10 US companies with the most aaigned/granted patents.

* **Answer**: International Business Machines Corporation (with 139091 patents in total). (Top 10 list below)

```{r patent_dominance}
library(reader)
library(data.table)

patent_dominance<-read_rds("patent_dominace.rds")
head(patent_dominance,10)
```


***

> 2.Patent Dominance: Recent patent acitivity: What US company had the most patents granted in 2019? List the top 10 companies with the most new granted patents for 2019.

* **Answer**: International Business Machines Corporation (with 9265 patents in 2019). (Top 10 list below)

```{r recent_patent_activity}
library(reader)
library(data.table)

recent_patent_activity<-read_rds("recent_patent_activity.rds")
head(recent_patent_activity,10)
```


***
> 3.Innovation in Tech: What is the most innovative tech sector? For the top 10 companies with the most patents, what are the top 5 USPTO tech main classes?

* **Answer**: Top 5 USPTO tech main classes for the top 10 companies with the most patents are "257", "438", "365", "370" and "358". (Top 10 list below)

```{r innovation_in_tech}
library(reader)
library(data.table)

innovation_in_tech<-read_rds("innovation_in_tech.rds")
head(innovation_in_tech,10)
```

***

